preprocessing

### 2022-11-14 r-imports/data.Rmd
lulucf fix

download.file("https://zenodo.org/record/6483002/files/essd_ghg_data_gwp100.xlsx?download=1","data-raw/gwp100.xlsx")

>>>>

download.file("https://zenodo.org/record/6483002/files/essd_ghg_data_gwp100.xlsx?download=1","data-raw/gwp100.xlsx")
download.file("https://zenodo.org/record/7190601/files/LULUCF%20NGHGI%20database%20August%202022.xlsx?download=1","data-raw/lulucf.xlsx")

library(httr)
url = "https://zenodo.org/record/7190601/files/LULUCF%20NGHGI%20database%20August%202022.xlsx?download=1"
GET(url, write_disk("data-raw/lulucf.xlsx", overwrite=TRUE))

### 2022-11-14 r-prep/prep.Rmd
lulucf fix

```{r}
data_gwp100 = read_excel("data-raw/essd_ghg_data_gwp100.xlsx",sheet = "data")
load("data-raw/data_wdi.RData") 
data_wdi %<>%
  select(-country)

data_base = data_gwp100 %>%
  left_join(data_wdi,by=c("ISO","year")) %>%
  mutate(GHG_pc = GHG/pop) %>%
  mutate(GDP_pc = gdp_ppp/pop) %>%
  filter(year <= 2019) %>% 
  mutate(EU= case_when(country %cin% eurostat::eu_countries[2]~ TRUE))

>>>>

```{r}
data_gwp100 = read_excel("data-raw/essd_ghg_data_gwp100.xlsx",sheet = "data")

#data_lulucf = read_excel("data-raw/lulucf.xlsx",sheet = "data")
data_lulucf = read_excel("data-raw/egr22_country_data.xlsx",sheet = "data") %>%
  rename(ISO = iso, co2_lulucf = CO2_LULUCF_NGHGI) %>%
  select(ISO, year, co2_lulucf)

load("data-raw/data_wdi.RData") 
data_wdi %<>%
  select(-country)

data_base = data_gwp100 %>%
  left_join(data_wdi,by=c("ISO","year")) %>%
  left_join(data_lulucf,by=c("ISO","year")) %>%
  mutate(GHG_pc = GHG/pop) %>%
  mutate(GDP_pc = gdp_ppp/pop) %>%
  filter(year <= 2019) %>% 
  mutate(
    EU = case_when(country %in% eurostat::eu_countries[2]$name~ TRUE, TRUE ~ FALSE),

  )
